\textls[-0]{\thetitle}

### 2023-03-23 metatheory-condensed.tex
fix

In rules \ruleref{l/add} and \ruleref{lsig/add},
the second premise $\goodTerm{\Gm, \mathit{self} : A}{t}{T}$ is
responsible for late binding.
Here, $A$ abstracts the context of the current field~$t$, controlling
how the types of the fields prior to~$t$ are exposed to the typing of~$t$.
Crucially, %unlike the second field in a dependent pair (\ruleref{tm/pair}),
the premise $\goodTerm{\Gm, \mathit{self} : A}{t}{T}$ makes clear that
the typing of~$t$ in \ruleref{l/add} is \emph{universally} quantified---%
rather than \emph{existentially} quantified as is in \ruleref{tm/pair}---%
over how the fields in $t$'s context are defined.
Late binding enables reuse.
A different linkage~$\ell'$ that overrides fields in $t$'s context (and thus models a derived family)
can reuse~$t$---without retyping it---by first
projecting~$t$ from $\LkgAdd{\lkg}{t}$ and then appending it to~$\lkg'$.
%\EDJ{I suggest change this sentence to `by projecting it out of parent linkage and adding it in the derived linkage'}.

@@

\item 
The next four fields model the four constructors of~\lsti{tm}.
Constructor \lsti{tm_unit} is modeled as $\Wsup{}{\wsig_{\texttt{tm}}}{\top}{\bot}$
and typed with $\El{\mathit{self}.\texttt{tm}}$, where $\mathit{self}$ stands for
the typing context containing the first field~\lsti{tm}.
The W-type signature $\wsig_{\texttt{tm}}$ is exposed in
this typing context; that is, \lsti{tm} has type $\TyS{\wcode{\wsig_{\texttt{tm}}}}$.
So $\El{\mathit{self}.\texttt{tm}}$ and $\El{\wcode{\wsig_{\texttt{tm}}}}$ can be equated,
as required by rule \ruleref{tm/wsup}.

>>>>

In rules \ruleref{l/add} and \ruleref{lsig/add},
the second premise $\goodTerm{\Gm, \mathit{self} : A}{t}{T}$ is
responsible for late binding.
Here, $A$ abstracts the context of the current field~$t$, controlling
how the types of the fields prior to~$t$ are exposed to the typing of~$t$.
Crucially, %unlike the second field in a dependent pair (\ruleref{tm/pair}),
the premise $\goodTerm{\Gm, \mathit{self} : A}{t}{T}$ makes clear that
the typing of~$t$ in \ruleref{l/add} is \emph{universally} quantified---%
rather than \emph{existentially} quantified as is in \ruleref{tm/pair}---%
over how the fields in $t$'s context are defined.
Late binding enables reuse.
A different linkage~$\ell'$ that overrides fields in $t$'s context (and thus models a derived family)
can reuse~$t$---without retyping it---by first
projecting~$t$ from $\LkgAdd{\lkg}{\mathit{self}.t}$ and then appending it to~$\lkg'$.
%\EDJ{I suggest change this sentence to `by projecting it out of parent linkage and adding it in the derived linkage'}.

@@

\item 
The next four fields model the four constructors of~\lsti{tm}.
Constructor \lsti{tm_unit} is modeled as $\Wsup{}{\wsig_{\texttt{tm}}}{\top}{x.\bot}$
and typed with $\El{\mathit{self}.\texttt{tm}}$, where $\mathit{self}$ stands for
the typing context containing the first field~\lsti{tm}.
The W-type signature $\wsig_{\texttt{tm}}$ is exposed in
this typing context; that is, \lsti{tm} has type $\TyS{\wcode{\wsig_{\texttt{tm}}}}$.
So $\El{\mathit{self}.\texttt{tm}}$ and $\El{\wcode{\wsig_{\texttt{tm}}}}$ can be equated,
as required by rule \ruleref{tm/wsup}.
